\begin{titlepage}
   \begin{center}
        \vspace*{-1cm}
        \begin{center}
        \textbf{THE IMPACT OF ELECTORAL DYNAMICS ON MUNICIPAL\\ FISCAL MANAGEMENT IN NEPAL}
    	\end{center}
        \vspace{3.5cm}
        
        \textbf{\large {A Thesis}} \\
        
        \textbf{Submitted to the 
        Central Department of Economics, \\
        Faculty of Humanities and Social Sciences, \\
        Tribhuvan University, Nepal,\\
        in Partial Fulfillment of the Requirements\\
        for the Degreee of}
        
        \vspace{3.5cm}
        
    
        \textbf{\emph{MASTER OF ARTS} \\
        \emph{in} \\
        \emph{ECONOMICS}}        
        \vspace{3.5cm}
        
        \textbf{BY \\
        Bibek Pokharel \\
        ROll No.: 90/078 \\
        Regd. No: 6-3-28-291-2020}   \\     
        \textbf{Central Department of Economics \\
        Kirtipur, Kathmandu, Nepal.}
        
        \vspace{2.5cm}
        
        \textbf{August, 2024}
        
    \end{center}
\end{titlepage}


\renewcommand{\contentsname}{Table of Contents} % it renames default content into table of contents


\pagenumbering{gobble}




\pagenumbering{gobble}
\newpage

%page i
\begin{center}
\textbf{\large Declaration}
\end{center}
\section*{}
\addcontentsline{toc}{section}{Declaration}


\vspace{-10mm}I, Bibek Pokharel, hereby declare that this thesis entitled \textbf{Electoral Influence on Fiscal Discipline : Analysis of  Economic and Fiscal Determinants of Nepal's Local Level Entities} submitted to the Central Department of Economics, Tribhuvan University, is my work prepared under the supervision of my supervisor, Dr. Resham Bahadur Thapa-Parajuli. I also certify that the thesis has been authored by me and helps that I have received in the research work and the preparation of this thesis have been acknowledged properly. Moreover, I attest that all information sources and literature used are indicated in the reference section and that no part of this thesis has either been submitted or accepted for any other degree at this or any other university or institution .\vspace{10mm}\\ 
\textbf{I will be solely responsible if any evidence is found against my declaration.} \\

\vspace{25mm}
\noindent
\begin{tabular}{@{}p{2.5in}p{2in}p{2in}@{}}
\hrulefill \\
\textbf{Bibek Pokharel} &&\\
\textbf{\today}\\
\end{tabular}

\pagenumbering{roman}
\setcounter{page}{2}


%page ii
\newpage
\begin{center}
\textbf{\large Letter of Recommendation}
\end{center}\section*{}

\addcontentsline{toc}{section}{Letter of Recommendation}

\vspace{-10mm}This thesis entitled \textbf{Electoral Influence on Fiscal Discipline : Analysis of  Economic and Fiscal Determinants of Nepal's Local Level Entities} has been prepared by Mr. Bibek Pokharel under my supervision. I hereby recommend this thesis for examination by the Thesis Committee as a partial fulfillment of the requirements for the Degree of \textbf{Master of Arts} in \textbf{Economics}.\vspace{15mm} \\

\begin{tabular}{@{}p{3in}p{2in}p{2in}@{}}
\hrulefill \\
\textbf{Dr.Resham Bahadur Thapa-Parajuli} &&\\
\textbf{Thesis Supervisor} &&\\
\textbf{\today}\\
\end{tabular}


%page iii
\newpage
\begin{center}
\textbf{\large Approval Sheet}
\end{center}
\section*{}
\addcontentsline{toc}{section}{Approval Sheet}

\vspace{-10mm}We certify that the thesis entitled \textbf{Electoral Influence on Fiscal Discipline : Analysis of  Economic and Fiscal Determinants of Nepal's Local Level Entities} submitted by \textbf{Mr.Bibek Pokharel} to the Central Department of Economics, Faculty of Humanities
and Social Sciences, Tribhuvan University, Nepal in partial fulfillment of the requirements
for the Degree of \textbf{MASTER OF ARTS} in \textbf{ECONOMICS} has been found satisfactory in
scope and quality. Therefore, we accept this thesis as a part of the said degree.\vspace{15mm}\\

\begin{tabular}{@{}p{2.5in}p{2in}p{2in}@{}}
\hrulefill \\
\textbf{Prof. Dr. HOD} &&\\
\textbf{(Head of Department)} &&\\
\end{tabular}\vspace{15mm}\\

\begin{tabular}{@{}p{2.5in}p{2in}p{2in}@{}}
\hrulefill \\
\textbf{Prof. Dr. external examiner} &&\\
\textbf{(External Examiner)} &&\\
\end{tabular}\vspace{15mm}\\

\begin{tabular}{@{}p{2.5in}p{2in}p{2in}@{}}\hrulefill \\
\textbf{Prof. Dr. Thesis Supervisor} &&\\
\textbf{(Thesis Supervisor)} &&\\
\end{tabular}\vspace{15mm}\\
\hspace{3mm}\textbf{\today}


%page iv
\newpage
\begin{center}
\textbf{\large Acknowledgements}
\end{center}
\section*{}
\addcontentsline{toc}{section}{Acknowledgements}

\vspace{-10mm} 
The list of people and institutions, who helped me in many aspects during the preparation of this thesis, is long and  I appreciate each of them. From brainstorming the initial idea to ultimately fine-tuning the minor details, my supervisor Dr. Resham Bahadur Thapa-Parajuli has helped me in each step of this thesis journey. I am grateful to call him my mentor. \\
Saman and Deepa were really helpful and handy in this hectic process and I can't thank them enough. I am thankful for the members of the department for various direct and indirect helps of varied types.\\
I also appreciate the unrecognized people whose works on free softwares helped, including CRAN for R software, \LaTeX{}, QGIS, and other anonymous helpers over the internet.\\
Finally, I thank my wife, Muna, who I first met while preparing for this thesis, for helping me complete it. I also hope that she complete her thesis in time.\\
.\vspace{5mm}\\ 
\textbf{Bibek Pokharel}\\
\textbf{Kathmandu, Nepal}\\
\textbf{\today}

%table of content page
\newpage
\begin{center}
\tableofcontents
\end{center}
\addcontentsline{toc}{section}{Table of Contents}

%list of table page
\newpage
\begin{center}
\listoftables

\section*{}
\addcontentsline{toc}{section}{List of Tables}

%list of figure page

\listoffigures
%\end{center} here if list of abbreviation needed in new page. also begin center on line 68 or  69
\section*{}
\addcontentsline{toc}{section}{List of Figures}

%list of abbreviations page

\newpage
\textbf{\large List of Abbreviations}
\end{center}
\section*{}
\addcontentsline{toc}{section}{List of Abbreviations}
\textbf{AG}\hspace{32mm}Auditor General\\
\textbf{CBS}\hspace{28mm} Central Bureau of Statistics\\
\textbf{COVID-19}\hspace{17mm}CoronaVirus Disease 2019\\
\textbf{DiD}\hspace{29mm} Difference-in-Differences\\
\textbf{FGT}\hspace{28mm} First Generation Theory\\
\textbf{GDP}\hspace{26mm} Gross Domestic Product\\
\textbf{NNRFC}\hspace{21mm}National Natural Resources and Financial Commission\\
\textbf{OECD}\hspace{23mm} Organization for Economic Cooperation and Development\\
\textbf{OLG}\hspace{28mm}Overlapping Generation\\
\textbf{OLS}\hspace{28mm}Ordinary Least Square\\
\textbf{SGT}\hspace{27mm} Second Generation Theory\\
\textbf{VDC}\hspace{26mm} Village Development Committee\\
\textbf{WB}\hspace{28mm} The World Bank\\






%abstract
\newpage
\begin{center}
\textbf{\large Abstract}
\end{center}
\section*{}
\addcontentsline{toc}{section}{Abstract}
\vspace{-10mm}
This study examines the relationship between the electoral behavior and the fiscal and economic discipline of the local governments of Nepal. The study has collected the electoral data from the local level election held in 2017 and the yearly data on fiscal and economic variables from 2017 to 2021 has also been collected. Descriptive and explanatory analyses are used to examine the state and relationship among the variables of interest. Cross-sectional and pooled regression has been carried with HHI, voter turnout, education level, power sharing, and status of local level, as independent variable whereas fiscal and economic variables of income and expenditure function as dependent variables.\\
The findings reveal that electoral competition, as measured by HHI, and educational level have highly significant association with the improvement in fiscal and economic variables. The study concludes with the recommendations for strengthening electoral competition, increasing the education level, and proper monitoring and evaluations of the local level governments of Nepal.\\
\textit{Keywords: Local-level governments, fiscal federalism, elections, accountability}
